---
title: "Analysis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Analysis}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

In this document, we do the analysis presented in the paper.

Currently, the analysis uses fake data.

## Setup

```{r}
library(testthat)
library(ggsignif)
```

## Reading the data

```{r}
ratings <- readr::read_csv("ratings.csv", show_col_types = FALSE)
n_ratings <- nrow(ratings)
```

There are `r n_ratings` ratings.

## Analysis

Connecting the ratings to the formations:

```{r}
songs <- dplyr::select(heyahmama::get_releases(), cd_title, song_title)
n_songs <- nrow(songs)
```

There are `r n_songs` songs.

```{r}
cds <- dplyr::select(heyahmama::get_cds(), cd_title, formation)
n_cds <- nrow(cds)
```

There are `r n_cds` CDs.

```{r}
songs_per_formation <- dplyr::select(merge(songs, cds), song_title, formation)
testthat::expect_equal(n_songs, nrow(songs_per_formation))
knitr::kable(head(songs_per_formation))
```

Add the formations to the ratings:

```{r}
ratings_per_formation <- dplyr::select(merge(ratings, songs_per_formation), formation, rating)
testthat::expect_equal(n_ratings, nrow(ratings_per_formation))
ratings_per_formation$formation <- as.factor(ratings_per_formation$formation)
knitr::kable(head(ratings_per_formation))
```

## Formations

There are two datasets:

- Dataset A: all 4 formations
- Dataset B: the first 3 formations

## 4 formations

### Plot distribution of ratings

General plotting function:

```{r}
plot_ratings <- function(ratings_per_formation) {
  ggplot2::ggplot(
    ratings_per_formation,
    ggplot2::aes(x = formation, y = rating)
  ) + ggplot2::geom_violin()  
}
```

Apply this to all ratings:

```{r}
p <- plot_ratings(ratings_per_formation)
p
```

### Order formations based on rating

Order formations by ratings:

```{r}
get_ordered_average_rating_per_formation <- function(ratings_per_formation) {
  n_formations <- length(unique(ratings_per_formation$formation))
  
  average_rating_per_formation <-
    ratings_per_formation |> 
    dplyr::group_by(formation) |> 
    dplyr::summarise(average_rating = mean(rating))
  testthat::expect_equal(n_formations, nrow(average_rating_per_formation))

  ordered_average_rating_per_formation <- 
    average_rating_per_formation |> 
    dplyr::arrange(dplyr::desc(average_rating))
  testthat::expect_equal(n_formations, nrow(ordered_average_rating_per_formation))

  ordered_average_rating_per_formation
}
```

```{r}

knitr::kable(
  get_ordered_average_rating_per_formation(
    ratings_per_formation
  )
)
```

## Statistics

Do the formations have different ratings?

General function:

```{r}
get_stats_table <- function(ratings_per_formation) {
  n_formations <- length(unique(ratings_per_formation$formation))
  n_combinations <- (n_formations * (n_formations - 1)) / 2
  alpha <- 0.05 / n_combinations

  p_values_table <- tibble::tibble(
    a = rep(NA, n_combinations), 
    b = NA, 
    p = NA,
    alpha = alpha
  )

  i <- 1
  for (lhs in seq(1, n_formations - 1)) {
    ratings_lhs <- ratings_per_formation[ratings_per_formation$formation == lhs, ]$rating
    for (rhs in seq(lhs + 1, n_formations)) {
      ratings_rhs <- ratings_per_formation[ratings_per_formation$formation == rhs, ]$rating
      p_value <- wilcox.test(ratings_lhs, ratings_rhs, alternative = "two.sided")$p.value
      testthat::expect_true(i >= 1)
      testthat::expect_true(i <= nrow(p_values_table))
      p_values_table$a[i] <- lhs
      p_values_table$b[i] <- rhs
      p_values_table$p[i] <- p_value
      i <- i + 1
    }
  }
  p_values_table$is_the_same <- p_values_table$p > alpha
  p_values_table
}
```

Applying it here:

```{r}
knitr::kable(get_stats_table(ratings_per_formation))
```

## Plot with significance indicators

General function:

```{r}
plot_ratings_with_indicators <- function(ratings_per_formation) {
  p <- plot_ratings(ratings_per_formation)
  t_all <- get_stats_table(ratings_per_formation)
  
  t <- t_all[t_all$is_the_same == FALSE, ]
  
  t$annotation <- scales::scientific(t$p, digits = 1)
  t$y_position <- seq(
    from = 11.0, 
    to = 11.0 + ((nrow(t) - 1) * 2.0),
    by = 2.0
  )
  p + ggsignif::geom_signif(
    data = t,
    ggplot2::aes(
      xmin = a,
      xmax = b,
      annotations = annotation,
      y_position = y_position
    ),
    manual = TRUE
  )
  
}
```

To these ratings

```{r plot_ratings_with_indicators_4}
plot_ratings_with_indicators(ratings_per_formation)
```

## 3 formations

```{r}
t <- ratings_per_formation[ratings_per_formation$formation != 4, ]
p <- plot_ratings(t)
p
```

```{r}
knitr::kable(
  get_ordered_average_rating_per_formation(t)
)
```

```{r}
t <- ratings_per_formation[ratings_per_formation$formation != 4, ]
knitr::kable(get_stats_table(ratings_per_formation = t))
```

```{r plot_ratings_with_indicators_3}
plot_ratings_with_indicators(t)
```
